\pkg{dataMaid}: your assistant for documenting supervised data quality screening in \proglang{R}

### 2017-11-09 latex/article_vol3.Rnw
Minor changes regarding typos etc and how figures are included.

\begin{figure}[tb]
\begin{center}
\frame{\includegraphics[width=7.5cm,page=2]{dataMaid_toyData.pdf}}
\frame{\includegraphics[width=7.5cm,page=3]{dataMaid_toyData.pdf}}
%\includepdf[pages={2}, pagecommand={}]{dataMaid_testData.pdf}
\end{center}
\caption{The two first pages of the report created by running \code{makeDataReport()} on the \code{toyData}
  dataset. First, a summary of the full dataset is given along with an overview of what checks were performed. Next, a summary of all the variables and whether or not they are problematic is provided. Larger versions of the pages can be seen in
  Appendix~\ref{sec:appendix1}.}
\label{fig:example1}
\end{figure}

\begin{figure}[tb]
\begin{center}
\frame{\includegraphics[width=7.5cm,page=4]{dataMaid_toyData.pdf}}
\frame{\includegraphics[width=7.5cm,page=5]{dataMaid_toyData.pdf}}
%\includepdf[pages={2}, pagecommand={}]{dataMaid_testData.pdf}
\end{center}
\caption{The third and fourth pages of the report created by running \code{makeDataReport()} on the \code{toyData}
  dataset. Here, we see a description of each variable in the dataset, consisting of a summary table, a visualization and an indication of what problems were flagged for the variable (if any). At last, a few lines of metadata about the \code{makeDataReport()} are included for enhancing reproducibility. Larger versions of the pages can be seen in
  Appendix~\ref{sec:appendix1}.}
\label{fig:example2}
\end{figure}

@@

\begin{figure}[tb]
\begin{center}
\frame{\includegraphics[width=7.5cm,page=1]{dataMaid_presidentData.pdf}}
\frame{\includegraphics[width=7.5cm,page=2]{dataMaid_presidentData.pdf}}\\
\end{center}
\caption{The front page and the first page of the data overview report for the \code{presidentData} dataset. Note that the report title has been customized (front page), \code{identifyLoners} has been removed from the checks performed on character variables ("Identify levels with <6 obs." is not checked for character variables in the table on page 1) and that variables of class \code{Name} have been set to be treated like \code{character} variables (page 1). Larger versions of the pages can be seen in
  Appendix~\ref{sec:appendix2}.}
\label{fig:bigExampleP01}
\end{figure}

\begin{figure}[tb]
\begin{center}
\frame{\includegraphics[width=7.5cm,page=3]{dataMaid_presidentData.pdf}}
\frame{\includegraphics[width=7.5cm,page=4]{dataMaid_presidentData.pdf}}
\end{center}
\caption{The second and third pages of the \code{presidentData} data report. We see that there are two \code{Name} variables in the overview on page 2 and see that these variables are indeed treated as \code{character} variables on page 3, as specified in the \code{makeDataReport} call by use of the \code{treatXasY} argument. Larger versions of the pages can be seen in
  Appendix~\ref{sec:appendix2}.}
\label{fig:bigExampleP23}
\end{figure}

\begin{figure}[tb]
\begin{center}
\frame{\includegraphics[width=7.5cm,page=5]{dataMaid_presidentData.pdf}}
\frame{\includegraphics[width=7.5cm,page=6]{dataMaid_presidentData.pdf}}
\end{center}
\caption{Part of the data overview report generated for the \code{presidentData} dataset. Here, we see pages 4 and 5 from the \textit{Variable list}. Larger versions of the pages can be seen in
  Appendix~\ref{sec:appendix2}.}
\label{fig:bigExampleP45}
\end{figure}

@@

% \section{Appendix A: cleaning the toyData data frame} \label{sec:appendix1}
\includepdf[pages=2, pagecommand={\section{Data report for the toyData dataset} \label{sec:appendix1}}, frame=true, noautoscale=true, scale=0.7]{dataMaid_toyData.pdf}
\includepdf[pages=3-4, pagecommand={}, frame=true, noautoscale=true, scale=0.7,pagecommand={}]{dataMaid_toyData.pdf}

\includepdf[pages=2, pagecommand={\section{Data report for the presidentData dataset} \label{sec:appendix2}}, frame=true, noautoscale=true, scale=0.7]{dataMaid_presidentData.pdf}
\includepdf[pages=3-6, pagecommand={}, frame=true, noautoscale=true, scale=0.7]{dataMaid_presidentData.pdf}

>>>>

\begin{figure}[tb]
\begin{center}
\frame{\includegraphics[width=7.5cm,page=2]{dataMaid_toyData_appA.pdf}}
\frame{\includegraphics[width=7.5cm,page=3]{dataMaid_toyData_appA.pdf}}
%\includepdf[pages={2}, pagecommand={}]{dataMaid_testData.pdf}
\end{center}
\caption{The two first pages of the report created by running \code{makeDataReport()} on the \code{toyData}
  dataset. First, a summary of the full dataset is given along with an overview of what checks were performed. Next, a summary of all the variables and whether or not they are problematic is provided. Larger versions of the pages can be seen in
  Appendix~\ref{sec:appendix1}.}
\label{fig:example1}
\end{figure}

\begin{figure}[tb]
\begin{center}
\frame{\includegraphics[width=7.5cm,page=4]{dataMaid_toyData_appA.pdf}}
\frame{\includegraphics[width=7.5cm,page=5]{dataMaid_toyData_appA.pdf}}
%\includepdf[pages={2}, pagecommand={}]{dataMaid_testData.pdf}
\end{center}
\caption{The third and fourth pages of the report created by running \code{makeDataReport()} on the \code{toyData}
  dataset. Here, we see a description of each variable in the dataset, consisting of a summary table, a visualization and an indication of what problems were flagged for the variable (if any). At last, a few lines of metadata about the \code{makeDataReport()} are included for enhancing reproducibility. Larger versions of the pages can be seen in
  Appendix~\ref{sec:appendix1}.}
\label{fig:example2}
\end{figure}

@@

\begin{figure}[tb]
\begin{center}
\frame{\includegraphics[width=7.5cm,page=1]{dataMaid_presidentData_appB.pdf}}
\frame{\includegraphics[width=7.5cm,page=2]{dataMaid_presidentData_appB.pdf}}\\
\end{center}
\caption{The front page and the first page of the data overview report for the \code{presidentData} dataset. Note that the report title has been customized (front page), \code{identifyLoners} has been removed from the checks performed on character variables ("Identify levels with <6 obs." is not checked for character variables in the table on page 1) and that variables of class \code{Name} have been set to be treated like \code{character} variables (page 1). Larger versions of the pages can be seen in
  Appendix~\ref{sec:appendix2}.}
\label{fig:bigExampleP01}
\end{figure}

\begin{figure}[tb]
\begin{center}
\frame{\includegraphics[width=7.5cm,page=3]{dataMaid_presidentData_appB.pdf}}
\frame{\includegraphics[width=7.5cm,page=4]{dataMaid_presidentData_appB.pdf}}
\end{center}
\caption{The second and third pages of the \code{presidentData} data report. We see that there are two \code{Name} variables in the overview on page 2 and see that these variables are indeed treated as \code{character} variables on page 3, as specified in the \code{makeDataReport} call by use of the \code{treatXasY} argument. Larger versions of the pages can be seen in
  Appendix~\ref{sec:appendix2}.}
\label{fig:bigExampleP23}
\end{figure}

\begin{figure}[tb]
\begin{center}
\frame{\includegraphics[width=7.5cm,page=5]{dataMaid_presidentData_appB.pdf}}
\frame{\includegraphics[width=7.5cm,page=6]{dataMaid_presidentData_appB.pdf}}
\end{center}
\caption{Part of the data overview report generated for the \code{presidentData} dataset. Here, we see pages 4 and 5 from the \textit{Variable list}. Larger versions of the pages can be seen in
  Appendix~\ref{sec:appendix2}.}
\label{fig:bigExampleP45}
\end{figure}

@@

% \section{Appendix A: cleaning the toyData data frame} \label{sec:appendix1}
\includepdf[pages=2, pagecommand={\section{Data report for the toyData dataset} \label{sec:appendix1}}, frame=true, noautoscale=true, scale=0.7]{dataMaid_toyData_appA.pdf}
\includepdf[pages=3-4, pagecommand={}, frame=true, noautoscale=true, scale=0.7,pagecommand={}]{dataMaid_toyData_appA.pdf}

\includepdf[pages=2, pagecommand={\section{Data report for the presidentData dataset} \label{sec:appendix2}}, frame=true, noautoscale=true, scale=0.7]{dataMaid_presidentData_appB.pdf}
\includepdf[pages=3-6, pagecommand={}, frame=true, noautoscale=true, scale=0.7]{dataMaid_presidentData_appB.pdf}
